Proposed Solution

### 2016-11-14 Ennan-Proposal/travis.tex
autocommit

\begin{figure}[!tbh]
  \centering
  \begin{tikzpicture}
    \draw (0,0) rectangle (6,3.7); 
    \node [align=left] at (1.5,2.9) {\footnotesize \textbf{Breaking Rules}: \\ \footnotesize node\_js $\le$ 0 \\ \footnotesize \ldots};
    \draw (1.6,0.2) rectangle (5,2.2);
    \node [align=left] at (3.3,1.3) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
  \end{tikzpicture}
  \caption{An example set of necessary and breaking rules if we have seen a failing file with {\footnotesize node\_js: 0}, and a passing file with {\footnotesize node\_js: 0.4.}}
  \label{fig:versionSL}
\end{figure}

>>>>

The breaking rules will describe the conditions for an incorrect file based on examples we have seen of incorrect files.
Likewise, the necessary rules will describe the conditions for a correct file based on examples we have seen of correct files.
As shown in Figure~\ref{fig:versionSL}, this can result in a space where a file may contain relations that cannot be classified as either breaking or necessary.
Part of the research task will be to find an optimal treatment for such cases.

\begin{figure}[!tbh]
  \centering
  \begin{tikzpicture}
    \draw (0,0) rectangle (7,3.7); 
    \node [align=left] at (1.5,2.9) {\footnotesize \textbf{Breaking Rules}: \\ \footnotesize node\_js $\le$ 0 \\ \footnotesize \ldots};
    \draw (2.3,0.2) rectangle (6.2,2.2);
    \node [align=left] at (3.9,1.4) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
  \end{tikzpicture}
  \caption{An example set of necessary and breaking rules if we have seen a failing file with {\footnotesize node\_js: 0}, and a passing file with {\footnotesize node\_js: 0.4.}}
  \label{fig:versionSL}
\end{figure}
